Named Entity Recognition on HTML as a web data extraction subtask

### 2018-09-23 tex/article.tex
Correções no paper.

Other approaches such as NoDoSE (\cite{Adelberg1998}) and Debye (\cite{Laender2002a}) 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. Web data extraction techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate tradeoff between the degree of automation and 
the precision and recall of the data extraction tool.

@@

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. We first introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And then
we explore neural network architectures.

@@

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as showed in Figure \ref{fig:rnn_network}.

@@

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
data from CONLL-2003 shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

\subsubsection{LSTM-CRF + CNN character representations}
\ref{sssec:lstm_crf_cnn}

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}, it receives
only character embeddings as inputs. The character representations generated by the CNN 
are combined with word level representations and then fed to the Bidirectional LSTM with
a CRF output layer described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
The character embeddings fed to the CNN had 30 dimensions that were randomly initialized.

@@

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
had 30 dimensions that were randomly initialized.

@@

This task would be similar to the task of labeling authors in comments.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1999}.

@@

The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
a description of the data files. The validation set was used in the early stopping validation strategy
on neural model and CRF training, while results were evaluated by comparing results in the test set.

@@

Twelve categorical features were also present with each token in the dataset. They 
are presented in table \ref{tab:features}.

@@

Table \ref{tab:experiment1f} shows the results on experiment 1 for models
that employed all the features described in Table \ref{tab:features}.
Conventional models like HMMs, and CRFs can become competitive with
the right selection of features and a good gazetteer, however they still lose
to the best neural model without features, demonstrating their inherent limitations.
We can also see that the self training strategy for HMMs improved the quality of 
the models significantly in all cases, boosting both precision and recall. Finally,
HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) also performed better in
comparison to regular HMMs.
The neural models also improved a little with the new features. The plain LSTM-CRF
model gets a closer performance to the models that employed neural character 
representations. A fact that hints that the LSTM and CNN character representations 
were able to learn at least part of the morphological features automatically in the
models with no features. So, when these features are added explicitly, the differences 
in performance become less noticeable.

@@

The second experiment aimed to evaluate the performance of sequence models when 
the amount of training data is small. The same training data used in Experiment 1 was
split into five non overlapping sets with 17 documents. Each model was trained once 
with each of the five sets and tested with the same test set used in Experiment 1. 
Seventeen documents seem to be a feasible amount of documents to label in most WDE 
tasks. The results for each model was averaged over the five runs.

Table \ref{tab:experiment2} shows the precision, recall and F1-score for the same models
used in Experiment 1, but in this case we only show results for the Test set.
As expected, we can see that the performance of all models with no features was reduced in comparison 
to Experiment 1. HMMs show a terrible performance while CRFs are not 
impacted as much by the reduction in the amount of training examples. Neural models
keep performing better, but they were unable to learn patterns as efficiently in
the smaller training sets. The neural models show a small standard deviation, what
points to the fact that they can retain a consistent performance between different training 
datasets. In this matter, the dropout layers are crucial to produce better generalizations 
and prevent overfitting.

@@

Finally, all the results presented in this section considered a dataset with a minimum
amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
for example, a model may miss a few named entities because it includes a punctuation sign
or an honorific at the start or end of a named entity. In fact, we can boost the F1-score up
by a few percentage points with some simple heuristics. However, these strategies would 
probably not apply to other NER on HTML tasks, so we did not include them in the results.

@@

In this paper we compared the performance of multiple sequence models in the task of
NER on HTML, introducing a novel dataset that is publicly available. We showed that
neural networks can be employed effectively to solve this task while demanding no 
feature engineering (F1-score of 0.8867), and they can retain acceptable performance 
even when the training data is dramatically reduced (F1-score of 0.8255), even though 
in this case the feature selection can become more meaningful. We found that there are 
two components to the most successful models: neural based character representations
constructed with convolutional neural networks or bidirectional LSTMs and joint modelling 
of the output labels provided by a linear chain CRF output layer. The effective recognition 
of named entities on HTML is an essential step in most general web data extraction methods. 
However it may also point to the possibility of constructing a truly flexible approach to
cross domain data extraction based on neural networks.

>>>>

Other approaches such as NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a} 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. Web data extraction techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate tradeoff between the degree of automation and 
the precision and recall of the data extraction tool.

@@

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. First, we introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. Then
we explore neural network architectures.

@@

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as shown in Figure \ref{fig:rnn_network}.

@@

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
data from the ConLL-2003 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

\subsubsection{LSTM-CRF + CNN character representations}
\label{sssec:lstm_crf_cnn}

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}, it receives
only character embeddings as inputs. The character representations generated by the CNN 
are combined with word level representations and then fed to the Bidirectional LSTM with
a CRF output layer described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
The character embeddings fed to the CNN have 30 dimensions that were randomly initialized.

@@

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
have 30 dimensions that were randomly initialized.

@@

This task would be similar to the task of labeling authors in comments
from many different sources or labeling authors in articles collected from many
publishing platforms. Another similar task would be NER on tweets. Because of the character
limitation present on tweets, we end up with constraints comparable to the ones
found in the NER on HTML task, so we expect similar systems to have comparable performances
on both of these tasks.

We collected 145 computer science faculty pages from 42 different countries in
multiple languages, although the English version was prefered when it was available.
We gathered faculty web pages randomly in proportion to
the number of universities in each country\footnote{A detailed list of universities can
be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format. That is, one word per line with empty lines representing
sentence boundaries. Sentence boundaries were determined by line break HTML tags
(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
Sentences that were more than 50 tokens were also split according to punctuation.

A proper HTML segmenter poses many challenges by itself.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1999}.

@@

The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
a description of the data files. The validation set was used in the early stopping validation strategy
for the neural netowrks and CRF training, while the performance was evaluated by comparing results in the test set.

@@

Thirteen categorical features were also associated with each token in the dataset. They 
are presented in Table \ref{tab:features}.

@@

Table \ref{tab:experiment1f} shows the results on Experiment 1 for models
that employed all the features described in Table \ref{tab:features}.
Conventional models like HMMs, and CRFs can become competitive with
the right selection of features and a good gazetteer, however they still lose
to the best neural model without features, demonstrating their inherent limitations.
We can also see that the self training strategy for HMMs improved the quality of 
the models significantly in all cases, boosting both precision and recall. Finally,
HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) also performed better in
comparison to regular HMMs.
The neural models also improved a little with the new features. The plain LSTM-CRF
model gets a closer performance to the models that employed neural character 
representations. It points to the fact that the LSTM and CNN character representations 
were able to learn at least part of the morphological features automatically in the
models with no features. So, when these features are added explicitly, the differences 
in performance become less noticeable.

@@

The second experiment aimed to evaluate the performance of sequence models when 
the amount of training data is small. The same training data used in Experiment 1 was
split into five non overlapping sets with 17 documents. Each model was trained once 
with each of the five sets and tested with the same test set used in Experiment 1. 
Seventeen documents seem to be a feasible amount of documents to label in most WDE 
tasks. The results for each model were averaged over the five runs.

Table \ref{tab:experiment2} shows the precision, recall and F1-score for the same models
used in Experiment 1, but in this case we only show results for the Test set.
As expected, we can see that the performance of all models with no features was reduced in comparison 
to Experiment 1. HMMs show a terrible performance while CRFs are not 
impacted as much by the reduction in the amount of training examples. Neural models
keep performing better, but they were unable to learn patterns as efficiently in
the smaller training sets, the best model achieves an F1 score of 0.7652 in contrast to
0.8815 with the entire dataset. The neural models show a small standard deviation, what
points to the fact that they can retain a consistent performance between different training 
datasets. In this matter, the dropout layers are crucial to produce better generalizations 
and prevent overfitting.

@@

Finally, all the results presented in this section considered a dataset with a minimum
amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
for example, a model may miss a few named entities because it includes a punctuation sign
or an honorific at the start or end of a named entity. In fact, we can boost the F1-score up
by a few points with some simple heuristics. However, these strategies are specific to this
NER on HTML problem.

@@

In this paper we compared the performance of multiple sequence models in the task of
NER on HTML, introducing a novel dataset that is publicly available. We showed that
neural networks can be employed effectively to solve this task while demanding no 
feature engineering (F1-score of 0.8867), and they can retain acceptable performance 
even when the training data is dramatically reduced (F1-score of 0.8255), even though 
in this case the feature selection becomes more meaningful. We found that there are 
two components to the most successful models: neural based character representations
constructed with convolutional neural networks or bidirectional LSTMs and joint modelling 
of the output labels provided by a linear chain CRF output layer. The effective recognition 
of named entities on HTML is an essential step in most general web data extraction methods. 
However it may also point to the possibility of constructing a truly flexible approach to
cross domain data extraction based on neural networks.
